On Secure Delegation of SampBQP with a Classical Client

### 2020-03-29 qpip.tex
Get ready for next round of feedbacks

We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
We now present our $\QPIP_1$ protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for computation of $C(x)$ and error parameter $\varepsilon$}\label{ProtoQPIP1}

	Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}, and
	$\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.

@@

	\begin{enumerate}
		\item The honest prover prepares $M=\varepsilon^{-8}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\varepsilon^{-3}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\varepsilon m$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise. We now show the completeness and soundness of $\PiSamp$.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon^{-1})$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$ and $\delta=2\varepsilon$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	Note that the ground state has $\abs{A}=n+T+\frac{T}{e}$ qubits.
	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}=\frac{todo}{todo}=O(\varepsilon).$$

	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I|p_j=\cV_\GS(\rho_j)<\frac{1}{2}-2\varepsilon}$ and its complement.

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
	then clearly $\Prob{Z\geq\frac{m}{2}-hm}<\Prob{Y\geq\frac{m}{2}-hm}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-hm}=\Prob{Y-\mu\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
	where $\mu=mp_y=\frac{m}{2}-2hm$ and $\delta=\frac{2h}{1-4h}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

	Now, for the other case, $j\notin J$, we have
	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr\left(H_{C'(x)}\rho_j}\right)<\varepsilon.$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}
	$$D(\rho_j, \ket{\phi_{C'(x)}})<\poly(\varepsilon)$$

@@

	The soundness errors at each step is $\poly(\varepsilon)$, so the conclusion follows.
\end{prf}

>>>>

@@

We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
We present our protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for the computation $C(x)$ with error parameter $\varepsilon$}
	\label{ProtoQPIP1}

	Inputs:
	\begin{itemize}
		\item Error parameter $\varepsilon\in(0, 1)$
		\item Input string $x\in\set{0, 1}^n$
		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}.
		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}.
		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}.
	\end{itemize}

	Pseudocode:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies \Ethan{This isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon^{-1})$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	Note that the ground state has $\abs{A}=n+T+\frac{T}{e}$ qubits.
	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\ln\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$:
	$$J=\set{j\in I|p_j<\frac{1}{2}-2\kappa}$$

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$

@@

	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
\end{prf}
